results

### 2022-04-13 code/analysis_code/particle_type.Rmd
fig updates

#PARTICLE TYPE FIGURE
```{r}
fig_part_type <- part_sum %>% ggplot(aes(x = name, y = value)) + 
  geom_col() + geom_text(aes(label = percent(value/559), vjust = -0.5), size = 3) + ylim(0,380) + guides(fill=guide_legend("Particle Type")) + labs(y = "No. of Particles", x = "") + theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1), axis.text.y=element_text(size=12))
plot(fig_part_type)

@@

# plot color data
fig_part_color <- color %>% ggplot(aes(x = Color, y = number, fill = Color)) + 
  geom_col() + geom_text(aes(label = percent(number/968), vjust = -0.5), size = 3) + ylim(0,460) + scale_fill_manual(values = c("Black" = "gray0", "Blue" = "royalblue2", "Green" = "seagreen2", "Other" = "orange1", "Red" = "red1", "TRN/White"= "gray61")) + labs(x = "", y = "Microplastic Composition") + labs(y = "No. of Particles")  + theme_bw() + theme(legend.position = "none")+ theme(axis.text.x = element_text(angle = 45, hjust=1))
plot(fig_part_color)
#stacked
#reorder

ggplot(data = color, aes(x = obs, y = number, fill = Color)) + geom_bar(stat = "identity", position = "fill") + scale_fill_manual(values = c("Black" = "gray0", "Blue" = "royalblue2", "Green" = "seagreen2", "Other" = "orange1", "Red" = "red1", "Transparent/White"= "gray61")) + labs(x = "", y = "Microplastic Composition") + guides(fill=guide_legend("Particle Color")) +
   geom_text(aes(label = percent(number/968)), size = 3, color = "white", position = position_fill(vjust = 0.5)) + theme_bw()+ theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
plot(fig_part_color)

>>>>

#PARTICLE TYPE FIGURE
```{r}
fig_part_type <- part_sum %>% ggplot(aes(x = name, y = value)) + 
  geom_col() + 
  geom_text(aes(label = percent(value/559), vjust = -0.5), size = 3) + 
  ylim(0,380) + 
  guides(fill=guide_legend("Particle Type")) + 
  labs(y = "No. of Particles", x = "") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust=1), 
        axis.text.y=element_text(size=12)) + 
  annotate("text", x = 5, y = 300, label = "n = 559")
plot(fig_part_type)

@@

# plot color data
fig_part_color <- color %>% ggplot(aes(x = Color, y = number, fill = Color)) +
  geom_col() + 
  geom_text(aes(label = percent(number/968), vjust = -0.5), size = 3) + 
  ylim(0,300) + 
  scale_fill_manual(values = c("Black" = "gray0", "Blue" = "royalblue2", "Green" = "seagreen2", "Other" = "orange1", "Red" = "red1", "TRN/White"= "gray61")) + labs(x = "", y = "Microplastic Composition") + 
  labs(y = "No. of Particles")  + 
  theme_bw() + 
  theme(legend.position = "none")+ 
  theme(axis.text.x = element_text(angle = 45, hjust=1), 
        axis.text.y = element_text(size = 12)) + 
  annotate("text", x = 2, y = 200, label = "n = 484")
plot(fig_part_color)
#stacked
#reorder

ggplot(data = color, aes(x = obs, y = number, fill = Color)) + geom_bar(stat = "identity", position = "fill") + scale_fill_manual(values = c("Black" = "gray0", "Blue" = "royalblue2", "Green" = "seagreen2", "Other" = "orange1", "Red" = "red1", "Transparent/White"= "gray61")) + labs(x = "", y = "Microplastic Composition") + guides(fill=guide_legend("Particle Color")) +
   geom_text(aes(label = percent(number/968)), size = 3, color = "white", position = position_fill(vjust = 0.5)) + theme_bw()+ theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y = element_text(size = 3)) 
plot(fig_part_color)

### 2022-04-13 code/analysis_code/results.Rmd
fig updates

#particle type = fig_part_type
#particle color = fig_part_color
quad1 <- ggarrange(hist_all, hist_season, fig_part_type, fig_part_color, nrow = 2, ncol = 2, labels = "AUTO", vjust = 1) 
#%>% ggexport(filename = here("results","manuscript_figures", "quad_1.png"))
plot(quad_1)

>>>>

#particle type = fig_part_type
#particle color = fig_part_color
quad1 <- ggarrange(hist_all, hist_season, fig_part_type, fig_part_color, nrow = 2, ncol = 2, labels = "AUTO", vjust = 1) 
#%>% ggexport(filename = here("results","manuscript_figures", "quad_1.png"))
plot(quad1)
